Human capital mediates natural selection in contemporary humans

### 2022-01-02 why-natural-selection.Rmd
Add a "further results" section in the appendix

We also examine selection effects among respondents' parents, using
information on respondents' number of siblings. Effect sizes of polygenic
scores are highly correlated across the two generations. Median-splitting
respondents by year of birth, we find little evidence of change in effect sizes
among either the parents' or the respondents' generation. We check whether 
selection effects differ by socio-economic status in the
parents' generation. We have no information about parents' income, so we use the
1971 Townsend deprivation score of respondents' birthplace as a proxy
[@townsend1987deprivation]. Results show the same pattern as for respondents:
effect sizes are larger and more often significant in the most deprived areas
(Appendix Figure \@ref(fig:plot-siblings-townsend)). Lastly, the siblings data 
lets us check for a "quantity-quality tradeoff" between
number of children (of respondents' parents) and number of grandchildren. We
do not find any: in fact, the correlation between *number of siblings* and 
*number of children* is positive ($\rho$ = `r sib_chn_cor$estimate`, 
$p < 2 \times 10^{-16}$).

@@

\clearpage
\FloatBarrier
## Selection effects on raw polygenic scores

@@

\FloatBarrier
\clearpage
## Genetic correlations with EA3

@@

>>>>

We also examine selection effects among respondents' parents, using
information on respondents' number of siblings. Effect sizes of polygenic
scores are highly correlated across the two generations. Median-splitting
respondents by year of birth, we find little evidence of change in effect sizes
among either the parents' or the respondents' generation. We check whether 
selection effects differ by socio-economic status in the
parents' generation. We have no information about parents' income, so we use the
1971 Townsend deprivation score of respondents' birthplace as a proxy
[@townsend1987deprivation]. Results show the same pattern as for respondents:
effect sizes are larger and more often significant in the most deprived areas
(Appendix Figure \@ref(fig:plot-siblings-townsend)); effects change
sign when controlling for AFLB (Appendix Figure \@ref(fig:plot-age-birth-parents)). Lastly, the siblings data 
lets us check for a "quantity-quality tradeoff" between
number of children (of respondents' parents) and number of grandchildren. We
do not find any: in fact, the correlation between *number of siblings* and 
*number of children* is positive ($\rho$ = `r sib_chn_cor$estimate`, 
$p < 2 \times 10^{-16}$).

@@

@@

@@

\clearpage
\FloatBarrier
## Further results
### Selection effects on raw polygenic scores

\FloatBarrier
\clearpage

### Genetic correlations with EA3
